abxD01 Paper

### 2015-03-25 PAPER.Rmd
Edit up to correlation analysis

![**Figure 1.**](results/figures/Figure1/figure1.png)

**Figure 1. Microbiota structures following diverse antibiotic treatments.** This figure shows the average percent relative abundances for family level phylotypes found in each experimental group on the day of *C. difficile* challenge. Each row depicts a different antibiotic perturbation. The level *C. difficile* colonization found 24 hours post microbiota sampling is indicated in the top right for each treatment. Error bars indicate standard error of the mean.

@@

> ### Figure 1: Bargraph
>
> This figure was built using the R script called "stacked.barcharts.r", which contains the stackedbarcharts() funciton in the abxD01 folder.The input files are listed in Github. The graph can be sorted 2 ways either by the untreated's decreasing relabund (sortbyphyl=FALSE), or by the most abundant within each phylum (sortbyphyl=TRUE). For each treatment, the resulting *C. difficile* CFU/g Feces is also labeled on the Y axis below the treatment name.
> The parameters I changed in the r script were:

```{r, eval=FALSE, warning=FALSE}
abx<-c("Untreated", "Ciprofloxacin", "Clindamycin", "Vancomycin", "Streptomycin", "Cefoperazone", "Ampicillin", "Metronidazole")

library(Hmisc)
stackedbarcharts(file="~/Documents/Github/abxD01/Figure1/abxD01.final.tx.2.subsample.relabund.topdose2.forlogscale.csv", fileIDS = "~/Documents/Github/abxD01/Figure1/topdose_tx2_barchart_ids.csv", graphLabels = abx, sortbyphyl = TRUE, graphbyphyl = FALSE)

> Files saved as "topdose2_tx1_sorted_10x20.pdf" and "topdose2_tx2_sorted_10x20.pdf".
>
> ### Supplemental Figure 1: correlation plot of diversity with *C. difficile*
>
> For the correlation calculations see the next section of the results.
> Figure making:

```
# In mothur:
summary.single(calc=invsimpson-shannon, shared=abxD01.final.an.unique_list.shared, subsample=1625)

```
> Using these results, I selected the samples within the original antibiotic set.  Then I calculated the spearman correlation of *C. difficile* CFU/g feces on day 1 with the level of diversity found in the community on day 0 (day of challenge). Both inverse simpson and shannon indices were included.

@@

>>>>

@@

@@

**Figure 1. Antibiotic treatments result in significant alterations to the structure of the microbiome and variation in colonization resistance.** The median percent relative abundances of the most abundant phyla found in each experimental group on the day of *C. difficile* challenge. Each bargraph depicts a different antibiotic perturbation. The median level *C. difficile* colonization found 24 hours post microbiota sampling is indicated in the top right for each treatment. Error bars indicate the interquartile range.
